Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-19 paper.tex
Add placeholder for turbine drawing

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine, but with higher solidity, or blade chord to radius ratio. Details
of the turbine and experimental setup are described in \cite{Bachant2015-JoT},
and a CAD model of the turbine is available from \cite{Bachant2014-RVAT-CAD}.

@@

\todo[inline]{Make sure to use drawing of turbine with no hubs, since these were
included in the tare drag}

>>>>

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine, but with higher solidity, or blade chord to radius ratio. Details
of the turbine and experimental setup, shown in Figure~\ref{fig:turbine} and
Figure~\ref{fig:exp-setup}, respectively, are described in
\cite{Bachant2015-JoT}, and a CAD model of the turbine is available from
\cite{Bachant2014-RVAT-CAD}.

\begin{figure}[ht!]
\caption{Drawing of the turbine model. Note that the upper and lower mounting
flanges have been excluded as these were included in the tare drag
measurements.} 
\label{fig:turbine}
\end{figure}

@@
